\documentclass[margin,11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
%\usepackage{geometry}
%\geometry{letter, top=1in, left=1in, right=1in, bottom=1in}

\usepackage{fontspec}
\setmainfont{Amiri}

\newlength\tindent
\setlength{\tindent}{10pt}
\topmargin=-0.25in

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------
\moveleft.5\hoffset\centerline{\large\bf Ben Olson}
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{2359 Wood Bridge Cove}
\moveleft.5\hoffset\centerline{Memphis, TN 38119}
\moveleft.5\hoffset\centerline{(901) 484-8654}
\moveleft.5\hoffset\centerline{matthew.olson@intel.com}

%----------------------------------------------------------------------------------------

\begin{resume}

% EDUCATION
\section{EDUCATION}
  {\textbf{University of Tennessee, Knoxville}} \hfill August, 2021 \\
    \textit{PhD Candidate in Computer Science} \\
    \hspace*{\tindent} Topic: Compiler and Runtime Software for Complex Memory Systems \\
    \hspace*{\tindent} Advisor: Dr. Michael R. Jantz \\
    \hspace*{\tindent} Awarded Tennessee Fellowship; \$40,000 over four years

  {\textbf{University of Tennessee, Knoxville}} \hfill July, 2015 \\
    \textit{Bachelor of Science in Computer Science} \\
    \hspace*{\tindent} Awarded Tennessee HOPE Scholarship with Merit \\
    \hspace*{\tindent} Awarded Volunteer Scholarship

% RESEARCH EXPERIENCE
\section{RESEARCH EXPERIENCE}

  {\textbf{Graduate Research Assistant}} \hfill June, 2015 - August, 2021 \\
   The University of Tennessee, EECS Department \\
   Advisor: Dr. Michael Jantz
    \begin{itemize} \itemsep -2pt
      \item Developed a compiler pass and runtime library to enable
            efficient utilization on heterogeneous memory technologies
      \item Designed and implemented multiple policies in the HotSpot Java
            Virtual Machine to control the placement of hot and cold data and
            reduce energy consumption on systems with multiple DRAM ranks
    \end{itemize}
    
  {\textbf{Graduate Research Intern}} \hfill July, 2019 - July, 2020 \\
   Intel Corporation \\
   Supervisor: Kshitij Doshi
    \begin{itemize} \itemsep -2pt
      \item Extended runtime techniques to optimize automatic profile-guided 
            memory placement on Optane DC Persistent Memory Modules
    \end{itemize}

  {\textbf{ASTRO Graduate Intern}} \hfill Jul, 2018 - Feb, 2019 \\
   Oak Ridge National Laboratory, CSR group \\
   Supervisor: Terry Jones
    \begin{itemize} \itemsep -2pt
      \item Implemented the high-level interface for the Simplified Interface
            to Complex Memory, part of the DOE Exascale Computing Project
    \end{itemize}

  {\textbf{ASTRO Graduate Intern}} \hfill Jan, 2018 - May, 2018 \\
   Oak Ridge National Laboratory, CSR group \\
   Supervisors: Graham Lopez and Oscar Hernandez
    \begin{itemize} \itemsep -2pt
      \item Developed novel offline and online profiling and analysis
            strategies for understanding application data usage
      \item Created runtime extensions and a custom memory allocator to
            incorporate memory usage profiles during heterogeneous memory
            management
    \end{itemize}


% PUBLISHED RESEARCH
\section{PUBLISHED\\RESEARCH}
  {M. Ben Olson, Brandon Kammerdiener, Michael R. Jantz, Kshitij A. Doshi, and Terry Jones. \textit{Online Application Guidance for Heterogeneous Memory Systems.} In the ACM Transactions on Architecture and Code Optimization (TACO), April 2022.} \\
  \\\\
  {T. Chad Effler, Brandon Kammerdiener, Michael R. Jantz, Saikat Sengupta, Prasad A. Kulkarni, Kshitij A. Doshi, and Terry Jones. \textit{Evaluating the Effectiveness of Program Data Features for Guiding Memory Management.} ACM/IEEE International Symposium on Memory Systems (MemSys) (2019).} \\
  \\\\
  {Olson, M. Ben, Tong Zhou, Michael R. Jantz, Kshitij A. Doshi, M. Graham Lopez and Oscar R. Hernandez. \textit{MemBrain: Automated Application Guidance for Hybrid Memory Systems.} 2018 IEEE International Conference on Networking, Architecture and Storage (NAS) (2018): 1-10. \\
  \textbf{Awarded Best Paper.}}
  \\\\
  {Olson, Matthew Benjamin, Joseph T. Teague, Divyani Rao, Michael R. Jantz, Kshitij A. Doshi and Prasad A. Kulkarni. \textit{Cross-Layer Memory Management to Improve DRAM Energy Efficiency.} TACO 15 (2018): 20:1-20:27.}


% OTHER EXPERIENCE
\section{OTHER EXPERIENCE}

  {\textbf{Graduate Teaching Assistant}} \hfill Spring, 2017 \\
   \textit{The University of Tennessee, EECS Department}
    \begin{itemize} \itemsep -2pt
      \item Led a lab section for CS140, an intermediate C++ course
      \item Wrote scripts to automate grading
    \end{itemize}

  {\textbf{Student System Administrator}} \hfill Nov., 2013 - May, 2015 \\
   \textit{The University of Tennessee Office of IT, Newton HPC Program}
    \begin{itemize} \itemsep -2pt
      \item Configured, compiled, and installed scientific codes
      \item Developed automated build system in Perl
    \end{itemize}

  {\textbf{Student Cluster Competition Participant}} \hfill June - Dec., 2013 - 2014 \\
   \textit{The National Institute for Computational Sciences}
    \begin{itemize} \itemsep -2pt
      \item Attended SuperComputing '13 and '14, won second place in 2014
      \item Constructed, configured, and optimized a cluster each year
    \end{itemize}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
